\addcontentsline{toc}{section}{\protect СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\sloppy
\begin{thebibliography}{}
    \bibitem{dlbook} Goodfellow I., Bengio Y., Courville A.
    Deep Learning [Электронный ресурс]. — MIT Press, 2016. — URL: \detokenize{http://www.deeplearningbook.org.}

    \bibitem{gradcam}
    Grad-CAM: Visual Explanations from Deep Networks via Gradient-Based Localization [Электронный ресурс] /
    R.R. Selvaraju, M. Cogswell, A. Das, R. Vedantam, D. Parikh, D. Batra //
    International Journal of Computer Vision. — 2019. — Vol. 128, № 2. — P. 336–359. — URL: \detokenize{http://dx.doi.org/10.1007/s11263-019-01228-7.}

    \bibitem{VorontsovML}
    Воронцов К.В. Курс лекций по машинному обучению [Электронный ресурс]. — URL: \detokenize{http://www.machinelearning.ru/wiki/index.php?title=Машинное_обучение_\%28курс_лекций\%2C_К.В.Воронцов\%29}

    \bibitem{backprop}
    Rumelhart D.E., Hinton G.E., Williams R.J. Learning representations by back-propagating errors [Электронный ресурс] // Nature. — 1986. — Vol. 323, № 6088. — P. 533–536. — URL: \detokenize{https://doi.org/10.1038/323533a0}

    \bibitem{batch}
    Ioffe S., Szegedy C. Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift [Электронный ресурс]. — 2015. — URL: \detokenize{https://arxiv.org/abs/1502.03167}

    \bibitem{dropout}
    Srivastava N., Hinton G., Krizhevsky A., Sutskever I., Salakhutdinov R. Dropout: A Simple Way to Prevent Neural Networks from Overfitting [Электронный ресурс] // Journal of Machine Learning Research. — 2014. — Vol. 15, № 56. — P. 1929–1958. — URL: \detokenize{http://jmlr.org/papers/v15/srivastava14a.html}

    \bibitem{alexnet}
    Krizhevsky A., Sutskever I., Hinton G.E. ImageNet Classification with Deep Convolutional Neural Networks [Электронный ресурс] // Advances in Neural Information Processing Systems / Под ред. F. Pereira, C.J. Burges, L. Bottou, K.Q. Weinberger. — Curran Associates,
    Inc., 2012. — Vol. 25. — URL: \detokenize{https://proceedings.neurips.cc/paper_files/paper/2012/file/}
    \detokenize{c399862d3b9d6b76c8436e924a68c45b-Paper.pdf}

    \bibitem{vggnet}
    Simonyan K., Zisserman A. Very Deep Convolutional Networks for Large-Scale Image Recognition [Электронный ресурс]. — 2015. — URL: https://arxiv.org/abs/1409.1556
\end{thebibliography}